Temporal Activity Detection in Untrimmed Videos with Recurrent Neural Networks

### 2016-10-15 paper.tex
Add one more contributor
Fixed erratas

\author{
    Alberto Montes \\
    Universitat Politècnica de Catalunya \\
    Barcelona, Spain \\
    \texttt{al.montes.gomez@gmail.com} \\
    \And
    Amaia Salvador \\
    Image Processing Group \\
    Universitat Politècnica de Catalunya \\
    Barcelona, Spain \\
    \texttt{amaia.salvador@upc.edu} \\
    \And
    Xavier Giro-i-Nieto \\
    Image Processing Group \\
    Universitat Politècnica de Catalunya \\
    Barcelona, Spain \\
    \texttt{xavier.giro@upc.edu} \\
}

@@

    This work proposes a simple pipeline to classify and temporally localize activities in untrimmed videos. Our system uses features from a 3D Convolutional Neural Network (3D-CNN) as input to train a a recurrent neural network (RNN) that learns to classify video clips of 16 frames. After clip prediction, we post-process the output of the RNN to assign a single activity label to each video, and determine the temporal boundaries of the activity within the video. We show how our system can achieve competitive results in both tasks with a simple architecture. We evaluate our method in the ActivityNet Challenge 2016, achieving a 0.5874 mAP and a 0.2237 mAP in the classification and detection tasks, respectively. Our code and models are publicly available at at: \url{https://github.com/imatge-upc/activitynet-2016-cvprw}

@@

Impressive progress has been reported in the recent literature for video classification~\cite{tran2014learning,tran2015deep,wang2015towards,yao2015describing}, which requires to assign a label for the input video. While this task is already challenging, it typically requires videos to be trimmed beforehand (i.e. the category is present in the entire video).
However, a video classification system should be able to recognize activities in untrimmed videos, and find the temporal segments in which they appear.
This second challenge has been recently proposed in the ActivityNet Challenge 2016~\cite{caba2015activitynet}, in which participants are asked to both provide a single activity for each video, as well as the temporal segment where the activity happened in the video.
% AMAIA: Amb això et refereixes que la tasca de detecció temporal es nova d'Activitynet? Ho he modificat una mica... No queda massa clar... Si és així, jo directament mencionaria la challenge i la citaria.
In order to face both these challenges at the same time, we propose a simple pipeline composed of a 3D-CNN that exploits spatial and short temporal correlations followed by a recurrent neural network which exploits long temporal correlations.

@@

Later on, 3D-CNNs were proposed in ~\cite{tran2014learning}, which were able to exploit short temporal correlations between frames and have demonstrated to work remarkably well for video classification~\cite{tran2014learning,tran2015deep}. 3D-CNNs have also been used for temporal detection in~\cite{shoutemporal}, where multi-stage 3D-CNN architecture is used to classify video segment proposals.

@@

We use the 3D-CNN model proposed in~\cite{tran2014learning} to extract features for all videos in the database. We split the videos in 16-frame clips and resize them to 171$\times$128 to fit the original model's desired input. Features from the second fully connected layer (fc6) are extracted for each video clip.

@@

\subsection{Recurrent Neural Network}
\label{sec:architecture}
Next, we design a network that takes a sequence of 3D-CNN-f6 features from a video, and returns a sequence of class probabilities for each element in the sequence. We use LSTM layers, followed with dropout with $p = 0.5$ and a fully connected layer with a softmax activation. Figure~\ref{fig:global_pipeline} shows the proposed architecture. Different configurations of the number of LSTM layers and the number of cells have been tested and will be reviewed in the following sections.

@@

%The recurrent network have the following architecture: \texttt{input(4096) - dropout(.5) - N $\times$ lstm(c) - dropout(.5) - softmax(K+1)}.

@@

\subsection{Post-Processing}
Given a video, the prediction of our model is sequence of class probabilities for each 16-frame video clip. From this output, we need to be able to predict the activity  and temporally localize it. We post-process the network's output to achieve that goal. First, to obtain the activity prediction for the whole video, we simply compute the mean over all video clips in the video. We then take the class with maximum predicted probability as the predicted class.

@@

To obtain the temporal localization of the predicted activity, we first apply a mean filter of $k$ samples to the predicted sequence to smooth the values through time (see equation~\ref{eq:smooth}). Then, the probability of activity (vs no activity) is computed for all samples of the sequence, being the activity probability the sum of all activity probabilities, and the no activity probability, the one assigned to the background class. Finally, a threshold $\gamma$ is set and all clips with probability higher than $\gamma$ are considered as part of the detected temporal segment for the previously assigned activity.

@@

\subsection{Results}

@@

In the future, we would like to extend the work training all the pipeline end-to-end, including the 3D-CNN and improve the accuracy obtained.

>>>>

\author{
    Alberto Montes \\
    Universitat Politècnica de Catalunya \\
    Barcelona, Spain \\
    \texttt{al.montes.gomez@gmail.com} \\
    \And
    Amaia Salvador \\
    Image Processing Group \\
    Universitat Politècnica de Catalunya \\
    Barcelona, Spain \\
    \texttt{amaia.salvador@upc.edu} \\
    \And
    Santiago Pascual \\
    TALP Research Center \\
    Universitat Politècnica de Catalunya \\
    Barcelona, Spain \\
    \texttt{santiago.pascual@tsc.upc.edu} \\
    \And
    Xavier Giro-i-Nieto \\
    Image Processing Group \\
    Universitat Politècnica de Catalunya \\
    Barcelona, Spain \\
    \texttt{xavier.giro@upc.edu} \\
}

@@

    This work proposes a simple pipeline to classify and temporally localize activities in untrimmed videos. Our system uses features from a 3D Convolutional Neural Network (C3D) as input to train a a recurrent neural network (RNN) that learns to classify video clips of 16 frames. After clip prediction, we post-process the output of the RNN to assign a single activity label to each video, and determine the temporal boundaries of the activity within the video. We show how our system can achieve competitive results in both tasks with a simple architecture. We evaluate our method in the ActivityNet Challenge 2016, achieving a 0.5874 mAP and a 0.2237 mAP in the classification and detection tasks, respectively. Our code and models are publicly available at at: \url{https://github.com/imatge-upc/activitynet-2016-cvprw}

@@

Impressive progress has been reported in the recent literature for video classification~\cite{tran2014learning,tran2015deep,wang2015towards,yao2015describing}, which requires to assign a label for the input video. While this task is already challenging, it has typically been explored with videos to be trimmed beforehand (i.e. the category is present in the entire video).
However, a video classification system should be able to recognize activities in untrimmed videos, and find the temporal segments in which they appear.
This second challenge has been recently proposed in the ActivityNet Challenge 2016~\cite{caba2015activitynet}, in which participants are asked to both provide a single activity for each video, as well as the temporal segment where the activity happened in the video.
% AMAIA: Amb això et refereixes que la tasca de detecció temporal es nova d'Activitynet? Ho he modificat una mica... No queda massa clar... Si és així, jo directament mencionaria la challenge i la citaria.
In order to face both these challenges at the same time, we propose a simple pipeline composed of a 3D-CNN that exploits spatial and short temporal correlations, followed by a recurrent neural network which exploits long temporal correlations.

@@

Later on, 3D-CNNs were proposed in~\cite{tran2014learning} (known as C3D), which were able to exploit short temporal correlations between frames and have demonstrated to work remarkably well for video classification~\cite{tran2014learning,tran2015deep}. C3D have also been used for temporal detection in~\cite{scnn_shou_wang_chang_cvpr16}, where multi-stage C3D architecture is used to classify video segment proposals.

@@

We use the C3D model proposed in~\cite{tran2014learning} to extract features for all videos in the database. We split the videos in 16-frames clips and resize them to 171$\times$128 to fit the input of the C3D model. Features from the second fully connected layer (fc6) are extracted for each video clip.

@@

\subsection{Recurrent Neural Network}
\label{sec:architecture}
We design a network that processes a sequence of C3D-f6 features from a video, and returns a sequence of class probabilities for each 16-frames clip. We use LSTM layers, trained with dropout with $p = 0.5$ and a fully connected layer with a softmax activation. Figure~\ref{fig:global_pipeline} shows the proposed architecture. Different configurations of the number of LSTM layers $N$ and the number of cells $c$ have been tested and are compared in Section~\ref{sec:resultats}. The recurrent network have the following architecture: \texttt{input(4096) - dropout(.5) - N $\times$ lstm(c) - dropout(.5) - softmax(K+1)} where $K$ is the number of activity classes at the dataset.

@@

@@

\subsection{Post-Processing}
Given a video, the prediction of our model is sequence of class probabilities for each 16-frame video clip. This output is post-processed to predict the activity class and temporally localize it.
First, to obtain the activity prediction for the whole video, we compute the average of the class probabilities over all video clips in the video.
We consider the class with maximum predicted probability as the predicted class.

@@

To obtain the temporal localization of the predicted activity class, we first apply a mean filter of $k$ samples to the predicted sequence to smooth the values through time (see equation~\ref{eq:smooth}).
Then, the probability of \textit{activity} (vs \textit{no activity}) is predicted for each 16-frames clip, being the \textit{activity} probability the sum of all probabilities of activity classes, and the \textit{no activity} probability, the one assigned to the background class.
Finally, only those clips with an \textit{activity} probability over a threshold $\gamma$ are kept and labeled with the previously predicted class.
Notice that, in our dataset, each video can only contain video segments of the same activity class.
%a threshold $\gamma$ is set and all clips with probability higher than $\gamma$ are considered as part of the detected temporal segment for the previously assigned activity.

@@

\subsection{Results}
\label{sec:resultats}

@@

In the future, we would like to extend the work training all the pipeline end-to-end, including the C3D and improve the accuracy obtained.
